\chapter{Model Fitting and Modifications}
In total, 36 data sets were taken at 2-4 mm-wavelength and at two temperatures (12 at $\sim$308 K and 24 at $\sim$343 K) . This, along with data taken at the centimeter-wavelength by Steffes et al. \cite{Steffes-2015} (10 data sets at $\sim$435 K, 10 data sets at $\sim$490 K, and 5 data sets at $\sim$550 K), were used in finding the best-fit model.

Before creating a new formalism for the absorption of SO$_2$ in a CO$_2$ atmosphere, analysis of previous models was conducted. The Van Vleck and Weisskopf Model (VVW) used by Fahd and Steffes \cite{Fahd-1991} with the new JPL rotational line catalog (Pickett, et al. \cite{Pickett-1998}) was found to fit 85.88\% of all 500 data points within $2\sigma$ uncertainty (95\% confidence). Consideration of the model analysis process and the final model are presented.
\input{./model/uncertainties}

\section{Model Analysis Process}

The models considered in this comparison are the Van Vleck-Weisshopf model (using coefficients from Fahd and Steffes \cite{Fahd-1991}) and the Ben-Reuven model as calculated by Suleiman et al. \cite{Suleiman-1996}. The comparison of these models are done using a L$_2$ norm analysis. 

The following compliance function was used to calculate the number of data points that each model encompassed,
\begin{equation}
\textbf{1}_{model}(\alpha) = \left\{
     \begin{array}{lr}
       1 & : |\alpha_{measured} - \alpha_{model}| \leq \sqrt{Err_{tot}^2 + Err_{cond}^2 }\\
       0 & : |\alpha_{measured} - \alpha_{model}| > \sqrt{Err_{tot}^2 + Err_{cond}^2 }
     \end{array}
   \right.
\end{equation}
where $\textbf{1}_{model}$ is the compliance function for each model, and $\alpha_{measured}$, $\alpha_{model}$ is the measured absorption and the calculated absorption, respectively. $Err_{tot}$ and $Err_{cond}$ are the systematic and conditional errors as described previously. The percentage of data points that each model encompasses can be calculated using,
\begin{equation}
Per_{model} = \frac{\sum_{i=1}^N \textbf{1}_{model}(\alpha_i)}{N}\times 100\%
\end{equation}
where $Per_{model}$ is the percentage of data points that the model fits and $N$ is the total number of data points. The final results are summarized in Table \ref{tab:model-comp}.

\begin{sidewaystable}[p]

\caption{The percentage of the measured data points within $2\sigma$ uncertainty of the different models}
  \begin{tabular}{l | c c | r}
  \hline
  \hline
  SO$_2$ opacity model & Centimeter-Wavelength (1-8 GHz) & Millimeter-Wavelength (80-150 GHz) &Total\\
  \hline
   Fahd and Steffes (1992)	 & 82.95\%	& 	88.89\% & 84.49\%\\%85.88\%\\
  Suleiman (1997)			 & 62.98\%	&	88.10\% & 70.37\%\\
  \hline
  \hline
  \end{tabular}
  \label{tab:model-comp}
\end{sidewaystable}

 
\input{./model/results}

\clearpage

\section{Suggested Model}
Results indicate that the models for the centimeter- and millimeter-wavelength opacity from SO$_2$ in a CO$_2$ atmosphere by Suleiman et al. \cite{Suleiman-1996} and Fahd and Steffes \cite{Fahd-1991} are both valid over the entire centimeter-and millimeter-wavelength range under simulated conditions for the upper atmosphere of Venus. Based on the percentage of data consistent with the models, we suggest the model from Fahd and Steffes \cite{Fahd-thesis}, but using the updated line catalog from Picket et al. \cite{Pickett-1998}. This model employs the Van Vleck-Weisskopf lineshape, and was developed from measurements of SO$_2$/CO$_2$ mixtures conducted at room temperature. As per their paper, we employ only the rotational line catalog to compute opacity. (JPL spectral line catalog, Pickett et al., \cite{Pickett-1998}). While both models perform well, the Fahd and Steffes \cite{Fahd-1991}  model appears to provide a slightly better fit to the overall data set. 

It should also be noted that because both models were derived from measurements conducted at pressures of 6 bars or less, no allowance for the compressibility of CO$_2$ is included in these models. When performing the best-fit analysis of high-pressure data \cite{Steffes-2015}, a correction factor for compressibility was computed and entered into the models (by simply dividing the measured partial pressure of CO$_2$ by the compressibility, Z). 

