\documentclass[12pt]{gatech-thesis}
\usepackage{amsmath,amssymb,latexsym,float,epsfig,subfigure,rotating,longtable}
\numberwithin{equation}{chapter}
\numberwithin{figure}{chapter}

\setcounter{secnumdepth}{2}

%%
%% This example is adapted from ucthesis.tex, a part of the
%% UCTHESIS class package...
%%
\title{THE MILLIMETER-WAVELENGTH SULFUR DIOXIDE ABSORPTION SPECTRA MEASURED UNDER SIMULATED VENUS CONDITIONS} %% If you want to specify a linebreak
                               %% in the thesis title, you MUST use
                               %% \protect\\ instead of \\, as \\ is a
                               %% fragile command that \MakeUpperCase
                               %% will break!
\author{Amadeo Bellotti}
\department{School of Electrical and Computer Engineering}

%% Can have up to six readers, plus principaladvisor and
%% committeechair. All have the form
%%
%%  \reader{Name}[Department][Institution]
%%
%% The second and third arguments are optional, but if you wish to
%% supply the third, you must supply the second. Department defaults
%% to the department defined above and Institution defaults to Georgia
%% Institute of Technology.

\principaladvisor{Professor Paul G. Steffes}
%\committeechair{Professor Ignatius Arrogant}
\firstreader{Professor Morris B. Cohen Reference}
\secondreader{Professor Andrew F. Peterson}
%\thirdreader{Professor Earl Grey}
%\fourthreader{Professor John Smith}
%\fifthreader{Professor Jane Doe}[Another Department With a Long Name][Another Institution]
%\setcounter{secnumdepth}{2}
\degree{Master of Science}

%% Set \listmajortrue below, then uncomment and set this for
%% interdisciplinary PhD programs so that the title page says
%% ``[degree] in [major]'' and puts the department at the bottom of
%% the page, rather than saying ``[degree] in the [department]''

%% \major{Algorithms, Combinatorics, and Optimization} 

\copyrightyear{2014}
\submitdate{May 2015} % Must be the month and year of graduation,
                         % not thesis approval! As of 2010, this means
                         % this text must be May, August, or December
                         % followed by the year.

%% The date the last committee member signs the thesis form. Printed
%% on the approval page.
%\approveddate{1 July 2010}
\approveddate{TBD}

\bibfiles{bibliography}

%% The following are the defaults
%%    \titlepagetrue
%%    \signaturepagetrue
%%    \copyrightfalse
%%    \figurespagetrue
%%    \tablespagetrue
%%    \contentspagetrue
%%    \dedicationheadingfalse
%%    \bibpagetrue
%%    \thesisproposalfalse
%%    \strictmarginstrue
%%    \dissertationfalse
%%    \listmajorfalse
%%    \multivolumefalse

\begin{document}
\bibliographystyle{gatech-thesis}
%%
\begin{preliminary}
\begin{dedication}
\null\vfil
{\large
\begin{center}
To my parents,\\\vspace{12pt}
Who were always putting education first.
\end{center}}
\vfil\null
\end{dedication}
%\begin{preface}
%Theses have elements.  Isn't that nice?
%\end{preface}
\begin{acknowledgements}
I would like to express my deepest gratitude to my adviser Professor Paul Steffes for his support and guidance throughout the course of this research. His consent wealth of knowledge, support, and patience helped me in completing this work. Although electromagnetism, and planetary remote sensing are not fields I would have seen myself working with during my undergraduate years. Dr. Steffes, eased me into it in a way I feel allowed me to grow and enjoy it. I would also like to thank my committee members Dr. Andrew R. Peterson and Dr. Morris Cohen for providing me with the time and effort in carefully reviewing my thesis work.

The success of the laboratory experiments was made possible as a results of many contributions. I wish to thank Dr. Kirtuthika Devaraj for creating and automating the millimeter-wavelength measurement system and Dr. Thomas Hanley for the data processing code. Both of these were utilized in this research work. 

The consent support and encouragement from my family has allowed me to pursue my goals throughout these years. I cannot thank them enough for pushing me to go to graduate school. 
\end{acknowledgements}
% print table of contents, figures and tables here.
\contents
% if you need a "List of Symbols or Abbreviations" look into
% gatech-thesis-gloss.sty.
\begin{summary}

\end{summary}
\end{preliminary}
%%

\include{./intro/intro}
%\include{./theory/theory}
\include{./labwork/labwork}
%\include{./prelim/prelim}
\include{./model/model}
\include{./rtm/rtm}
\include{./summary/summary}

%\nocite{*}
%% We need this since this file doesn't ACTUALLY \cite anything...
%%
\appendix
\include{./refractivity/refract}

\begin{postliminary}
\references
%\postfacesection{Index}{%
%%             ... generate an index here
%%         look into gatech-thesis-index.sty
%}
%\begin{vita}
%Perry H. Disdainful was born in an insignificant town
%whose only claim to fame is that it produced such a fine
%specimen of a researcher.
%\end{vita}
\end{postliminary}

\begin{abstract}
The objective of the proposed research is to develop a mathematical model that accurately estimates the opacity of sulfur dioxide in a carbon dioxide atmosphere under conditions characteristic of the Venus troposphere based on extensive laboratory measurements. High precision measurements of the millimeter-wavelength properties of sulfur dioxide are being conducted under multiple pressure and temperatures. These measurements are being conducted in both W-band and F-band (2-3 and 3-4 millimeter-wavelengths). The results of this research will significantly improve the understanding of the millimeter-wavelength emission spectrum of Venus and possibly determine the source of variations in the Venus millimeter-wavelength emissions. 
\end{abstract}

\end{document}
